---
output:
  pdf_document: 
    toc: yes
    number_sections: yes
  html_document: default
editor_options:
  chunk_output_type: console
---
# Results

## Description

Import data

```{r Natura data import, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
SoftTraits <- read_excel("Natura_data/DRYER_infocollect_morpho.xlsx", 
  
                         
                         
      col_types = c("skip", "skip", "numeric", 
        "skip", "text", "text", "skip", "skip", 
        "text", "text", "skip", "skip", "skip", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", "numeric",
        "skip", "skip", "skip"))

SoftTraits <- SoftTraits %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

SoftTraits$name <- paste(SoftTraits$Genus, SoftTraits$Species)


```


Leaf thickness

```{r Natura- Leaf thickness, echo=FALSE, message=FALSE, warning=FALSE}
l1 <- ggplot(SoftTraits) +
  aes(x = name, y = MeanLeafThickness, fill = name) +
  geom_boxplot(shape = "circle") +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_fill_hue(direction = 1) +
  labs(
    title = "Mean leaf thickness",
    subtitle = " in natura",
    x = "Species",
    y = "Mean leaf thickness (mm)" ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    )
  )
```


Seedling heights

```{r Natura - Seedling height, echo=FALSE, message=FALSE, warning=FALSE}

library(ggplot2)

SoftTraits <- SoftTraits %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

SoftTraits$name <- paste(SoftTraits$Genus, SoftTraits$Species)

p1 <- ggplot(SoftTraits) +
  aes(x = name, y = `Height (cm)`, fill = name) +
  geom_boxplot(shape = "circle") +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_fill_hue(direction = 1) +
  labs(
    title = "Height of the seedlings",
    subtitle = " in natura",
    x = "Species") +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    )
  )


```

Stem diameter
```{r Natura - stem diameter, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)

SoftTraits <- SoftTraits %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

SoftTraits$name <- paste(SoftTraits$Genus, SoftTraits$Species)

p2 <- ggplot(SoftTraits) +
  aes(x = name, y = `Stem_diameter (mm)`, fill = name) +
  geom_boxplot(shape = "circle") +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_fill_hue(direction = 1) +
  labs(
    title = "Stem diameter of the seedlings",
    subtitle = " in natura",
    x = "Species") +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    )
  )
```



$\pi_{TLP}$

```{r Natura- Ptlp, echo=FALSE, fig.cap="$\\pi_{TLP}$.", message=FALSE, warning=FALSE}
library(ggplot2)
library(ggpubr)
library(dplyr)

Ptlp <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/15unEUBxCQz_2ekJPEkL6M5C12tjvFJ0P7nb0iLh6Caw/edit#gid=0")

Ptlp$Species_Name[Ptlp$Species_Name == "Epe.fal"] <- "falcata"
Ptlp$Species_Name[Ptlp$Species_Name == "Iry.hos"] <- "hostmannii"
Ptlp$Species_Name[Ptlp$Species_Name == "Jac.cop"] <- "copaia"
Ptlp$Species_Name[Ptlp$Species_Name == "Pte.off"] <- "officinalis"
Ptlp$Species_Name[Ptlp$Species_Name == "Sym.glo"] <- "globulifera"
Ptlp$Species_Name[Ptlp$Species_Name == "Tac.mel"] <- "melinonii"
Ptlp$Species_Name[Ptlp$Species_Name == "Vir.sur"] <- "surinamensis"

Ptlp <- Ptlp %>% mutate(Genus = "")

Ptlp <- Ptlp %>%
  mutate(Genus = case_when(
    Species_Name == 'falcata' ~ 'Eperua',
    Species_Name == 'hostmannii' ~ 'Iryanthera',
    Species_Name == 'copaia' ~ 'Jacaranda',
    Species_Name == 'officinalis' ~ 'Pterocarpus',
    Species_Name == 'globulifera' ~ 'Symphonia',
    Species_Name == 'melinonii' ~ 'Tachigali',
    Species_Name == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

Ptlp$name <- paste(Ptlp$Genus, Ptlp$Species_Name)


shapiro.test(Ptlp$Ptlp) # W = 0.96004, p-value = 0.06093 meets the normality assumption.

logPtlp<- log10(abs(Ptlp$Ptlp))

shapiro.test(logPtlp) # W = 0.97547, p-value = 0.3089 way better

Ptlp$name <- as.factor(Ptlp$name)

compare_means(Ptlp ~ name, data = Ptlp, method = "t.test", paired = FALSE)

modelPtlp <- lm(Ptlp ~ name, data = Ptlp)
summary(modelPtlp)

library(hrbrthemes)

# my data 
#Ptlp %>% 
  
  # Add a column called 'type': do we want to highlight the group or not?
  #mutate( type=ifelse(Ptlp< -1.76,"Highlighted","Normal")) %>%
  
  # Build the boxplot. In the 'fill' argument, give this column
  #ggplot( aes(x=name, y=Ptlp, fill=type, alpha=type)) + 
  #  geom_boxplot() +
   # scale_fill_manual(values=c("#69b3a2", "grey")) +
    #scale_alpha_manual(values=c(1,0.1)) +
    #theme_ipsum() +
    #theme(legend.position = "none") +
    #xlab("")

h1 <- ggplot(Ptlp) +
  aes(x = name, y = Ptlp, fill = name) +
  geom_boxplot(shape = "circle") +
  theme_minimal()+ 
  stat_compare_means(method = "anova", label.y=-1.4)+
  stat_compare_means(label = "p.signif", method = "t.test",
                     ref.group = "Eperua falcata") +
  scale_fill_hue(direction = 1) +
  labs(
    title = "Turgor loss point of the seedlings",
    subtitle = " in natura",
    x = "Species",
    y = "Turgor loss point (MPa)" ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    ),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 30, vjust = 1, hjust=1)
  )
```

 $\frac{Fv}{Fm} in natura$

```{r FvFm, echo=FALSE, fig.cap="$\\frac{Fv}{Fm}$.", message=FALSE, warning=FALSE}
library(readxl)
FvFm <- read_excel("Natura_data/3_FvFm/DRYER_FvFm.xlsx")
fvfm <-ggplot(FvFm) +
  aes(x = spName, y = `FvFm`) +
  geom_boxplot(shape = "circle", fill = "#2BDD1A") +
  theme_minimal()
fvfm
```

 LSWC

```{r measureRWC, echo=FALSE, fig.cap="$RWC$.", message=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)

LSWC <- read_excel("Natura_data/1_RWC/DRYER_RWC.xlsx")

LSWC <- mutate(LSWC, LSWC=(SW-DW)/DW)

LSWC$Species_Name[LSWC$Species_Name == "Epe.fal"] <- "falcata"
LSWC$Species_Name[LSWC$Species_Name == "Iry.hos"] <- "hostmannii"
LSWC$Species_Name[LSWC$Species_Name == "Jac.cop"] <- "copaia"
LSWC$Species_Name[LSWC$Species_Name == "Pte.off"] <- "officinalis"
LSWC$Species_Name[LSWC$Species_Name == "Sym.glo"] <- "globulifera"
LSWC$Species_Name[LSWC$Species_Name == "Tac.mel"] <- "melinonii"
LSWC$Species_Name[LSWC$Species_Name == "Vir.sur"] <- "surinamensis"

LSWC <- LSWC %>% mutate(Genus = "")

LSWC <- LSWC %>%
  mutate(Genus = case_when(
    Species_Name == 'falcata' ~ 'Eperua',
    Species_Name == 'hostmannii' ~ 'Iryanthera',
    Species_Name == 'copaia' ~ 'Jacaranda',
    Species_Name == 'officinalis' ~ 'Pterocarpus',
    Species_Name == 'globulifera' ~ 'Symphonia',
    Species_Name == 'melinonii' ~ 'Tachigali',
    Species_Name == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

LSWC$name <- paste(LSWC$Genus, LSWC$Species_Name)


shapiro.test(LSWC$LSWC) # W = 0.96004, p-value = 0.001 does not meet the normality assumption. wilcoxon test


 h2 <- ggplot(LSWC) +
  aes(x = name, y = LSWC, fill = name) +
  geom_boxplot(shape = "circle") +
  theme_minimal()+ 
  scale_fill_hue(direction = 1) + 
  labs(
    title = "Leaf saturated water content",
    subtitle = " in natura",
    x = "Species",
    y = "LSWC (g/g)" ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    ),
    axis.text = element_text(size = 15),
    axis.text.x = element_text(angle = 30, vjust = 1, hjust=1)
  )
```


Gmin
Leaf area

I used following code in `ImageJ`:

```{bash imageJsoft, eval=F, echo=T}
run("8-bit");
setAutoThreshold("Default");
//run("Threshold...");
setAutoThreshold("Default");
setOption("BlackBackground", false);
run("Convert to Mask", "method=Default background=Light calculate");
run("Analyze Particles...", "size=1000000-Infinity display summarize");
setAutoThreshold("Default dark");


```


```{r Natura : leaf area, echo=FALSE, warning=FALSE}

LeafArea <- read_excel("Natura_data/2_gmin/LeafAreaFinalResultsDRYERnatura.xlsx", col_types = c("text", "text", "skip",        "numeric", "skip", "skip", "skip", "skip"))

LeafArea$Species[LeafArea$Species == "Epe.fal"] <- "falcata"
LeafArea$Species[LeafArea$Species == "Iry.hos"] <- "hostmannii"
LeafArea$Species[LeafArea$Species == "Jac.cop"] <- "copaia"
LeafArea$Species[LeafArea$Species == "Pte.off"] <- "officinalis"
LeafArea$Species[LeafArea$Species == "Sym.glo"] <- "globulifera"
LeafArea$Species[LeafArea$Species == "Tac.mel"] <- "melinonii"
LeafArea$Species[LeafArea$Species == "Vir.sur"] <- "surinamensis"

LeafArea <- LeafArea %>%
  mutate(Genus = "")

LeafArea <- LeafArea %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

LeafArea$name <- paste(LeafArea$Genus, LeafArea$Species)

LeafArea <- LeafArea %>% filter(!Code %in% "58")
LeafArea <- LeafArea %>% filter(!Code %in% "36")


l2<- ggplot(LeafArea) +
  aes(x = name, y = LeafArea_cm2, fill = name) +
  geom_boxplot(shape = "circle") +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  scale_fill_hue(direction = 1) +
  labs(
    title = "Leaf area",
    subtitle = " in natura",
    x = "Species",
    y = "Leaf area (cm²)" ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5
    )
  )

```
 
```{r Natura : gmin, echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(ggplot2)

Gmin <- read_csv("Natura_data/2_gmin/Gmin_DRYERwithLA.csv", 
    col_types = cols(idTree = col_skip(), 
        beta = col_skip(), file = col_skip()))

shapiro.test(Gmin$gmin.slope_function) # W = 0.96004, p-value = 0.001 does not meet the normality assumption.


h3 <- Gmin %>%
 filter(gmin.slope_function >= 0.3 & gmin.slope_function <= 5.6) %>%
 ggplot() +
  aes(x = specCode, y = gmin.slope_function, fill = specCode) +
  geom_boxplot(shape = "circle") +
  scale_fill_hue(direction = 1) +
  labs(
    x = "Species",
    y = "Minimal conductance (mmol.m-2.s-1)",
    fill = "Species"
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(size = 15L),
    axis.title.x = element_text(size = 15L)
  )


```

*I deliberately removed 3 point (1 tac.mel and 2 sym.glo because gmin was really high - have to check data)*


Root:shoot ratio

```{r rootshoot ratio natura, echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4)


RootShoot_excel<- read_sheet("https://docs.google.com/spreadsheets/d/13NVmdKXHo6wZKErSje-4_Iv8C-6uHz_KuBTiUL6oifE/edit#gid=783989826", range = "traits") 



library(ggplot2)

p3 <- ggplot(RootShoot_excel) +
 aes(x = Name, y = RootShoot, fill = Name) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 labs(y = "Root to shoot ratio ", title = "Root to shoot ratio") +
 theme_minimal()+
  theme(legend.position = "none",axis.text.x = element_text(angle = 30, vjust = 1, hjust=1), plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5))

```

Specific root length 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(googlesheets4)

SRL <- read_sheet("https://docs.google.com/spreadsheets/d/13NVmdKXHo6wZKErSje-4_Iv8C-6uHz_KuBTiUL6oifE/edit#gid=27160926", range = "traits")


library(ggplot2)

p4 <-ggplot(SRL) +
 aes(x = Name, y = SRL, fill = Name) +
 geom_boxplot(shape = "circle") +
 scale_fill_hue(direction = 1) +
 labs(title = "Specific root length",subtitle = " in natura", x = " ", y = "Specific root length (cm.g-1)") +
 theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 30, vjust = 1, hjust=1), plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(
      face = "italic",
      hjust = 0.5))

library(plotly)

plot_ly(data = SRL, y = ~SRL, x=~Name, type = "box")
```


## Analyses

#### PCA

```{r DRYER-natura PCA, echo=FALSE, message=FALSE, warning=FALSE}
library(FactoMineR)
library(Factoshiny)
library(factoextra)

data <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/13NVmdKXHo6wZKErSje-4_Iv8C-6uHz_KuBTiUL6oifE/edit#gid=27160926", range = "traits")

data$LT 

#resultPCA <- Factoshiny(data[,c(3:6,10,11,13,14,20,21,22,23,27,28)])

res.PCA<-PCA(data[, c(3:6, 10, 11, 13, 14, 15, 24, 28)][,-c(1,2,3)],quali.sup=c(1),graph=FALSE)

#res.PCA<-PCA(data[, c(3:6, 10, 11, 13, 14, 20, 21, 22, 23, 27, 28)][,-c(1,2,3)],quali.sup=c(1),graph=FALSE)
plot.PCA(res.PCA,choix='var',habillage = 'none',cex=1.55,cex.main=1.55,cex.axis=1.55,title="Graph of the different variables")
plot.PCA(res.PCA,invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=1.6,cex.main=1.6,cex.axis=1.6,col.quali='#00FF40',label =c('quali'))

fviz_pca_var(res.PCA, col.var="steelblue")+
 theme_classic()

fviz_pca_ind(res.PCA,
             geom.ind = "point", # Montre les points seulement (mais pas le "text")
             col.ind = data$Name, # colorer by groups
             palette = c("#ff00ff", "#14c6de", "#ff6f00", "#14c6de", "#00ff1e", "#ff0000", "#2b8fed"),
             addEllipses = TRUE, # Ellipses de concentration
             legend.title = "Groups",
             ellipse.type = "confidence"
)+ theme_classic() + scale_shape_manual(values =c(16,16,16,16,16,16,16))

#fviz_pca_ind(res.PCA,
             geom.ind = "point", # Montre les points seulement (mais pas le "text")
             col.ind = data$Name, # colorer by groups
             palette = c("#ff00ff", "#14c6de", "#ff6f00", "#14c6de", "#00ff1e", "#ff0000", "#2b8fed"),
             addEllipses = TRUE, # Ellipses de concentration
             legend.title = "Groups",
             ellipse.type = "confidence"
)+ theme_classic() + scale_shape_manual(values =c(16,16,16,16,16,16,16))

#Rdim 3 et 4
res.PCA<-PCA(data[, c(2:6, 10, 11, 13, 14, 20, 21, 22, 23, 27, 28)][,-c(2,3,4)],quali.sup=c(2),graph=FALSE)
plot.PCA(res.PCA,axes=c(3,4),choix='var',habillage = 'contrib',title="Graphe des variables de l'ACP")
plot.PCA(res.PCA,axes=c(3,4),invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=1.2,cex.main=1.2,cex.axis=1.2,col.quali='#11FF00',label =c('quali'))

```


#### Plant morphology

```{r Natura morpho, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
#p1 plant height 
#p2 plant stem diameter
#p3 root to shoot ratio
#p4 SRL

plot_grid(p1, p2, p3, p4, labels = c('A', 'B', 'C', 'D'), label_size = 12)
```


#### Morphology of the leaf

```{r natura leaf morpho, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
#l1 leaf thickness
#l2 leaf area

plot_grid(l1, l2, labels = c('A', 'B'), label_size = 12)
```

#### Leaf hydraulic traits

```{r natura leaf hydrualics, echo=FALSE, message=FALSE, warning=FALSE}

library(ggplot2)
library(cowplot)
#h1 Pltp
#h2 lswc
#h3 gmin
plot_grid(h1, h2, labels = c('A', 'B'), label_size = 12)
plot(h3)

```

#### Covariation


```{r}
library(dplyr)


dplyr::select(data, RootShoot, Height, StemDiameter, LA, LSWC, Ptlp, gmin, LT, SRL) %>% 
  cor(use="pairwise.complete.obs") %>% 
  corrplot::corrplot.mixed()  
```


### Soil analysis

```{r soil analysis, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(dplyr)
library(tidyverse)
library(ggplot2)

analyses_sol <- read_excel("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/DRYER/Soil/analyses_sol.xls", sheet = "Feuil1")

analyses_sol <- analyses_sol %>% mutate(`sable(%)` = `Sables fins(%)` + `Sables grossiers(%)` , `limon(%)` = `Limons fins(%)` + `Limons grossiers(%)`)

sample <- c(rep("Greenhouse" , 3) , rep("Paracou" , 3))
soil_type <- rep(c("sable" , "limon" , "argile") , 2)
value <- c(85.3,7.7,7,83.2,7.1,9.7)
data <- data.frame(sample,soil_type,value)
 
# Stacked

ggplot(data, aes(fill=soil_type, y=value, x=sample)) + 
    geom_bar(position="fill", stat="identity")


library(ggplot2)

ggplot(analyses_sol) +
 aes(x = `Code Echantillon`, weight = `P-PO4(mg/kg)`) +
 geom_bar(fill = "#BF7C2A") +
 labs(x = "Echantillon", y = "P-PO4 (mg/kg)", title = "Phosphore assimilable ", subtitle = "(Olsen)") +
 theme_minimal()


```

```{r}

library(readxl)
library(dplyr)
library(tidyverse)
library(gt)
library(glue)
library(webshot2)
library(kableExtra)

analyses_sol <- read_excel("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/DRYER/Soil/analyses_sol.xls",
sheet = "Feuil2")

analyses_sol <- analyses_sol[-c(7:11), ] 
analyses_sol <- analyses_sol[-c(19:20), ] 
analyses_sol <- analyses_sol %>% select(-Greenhouse)

analyses_sol_table <- gt(analyses_sol)

analyses_sol$`Soil Tests`[9] <- paste0(analyses_sol$`Soil Tests`[9], 
                                footnote_marker_symbol(1))

analyses_sol$Paracou <- as.numeric(analyses_sol$Paracou) %>% round(digits = 2)

kbl(analyses_sol, caption ="Soil composition of seasonally flooded soils of Paracou.\\\\
\\Analyses performed on composite samples 8 different locations in Paracou. Soil samples were collected in the 0-10 cm horizon.", escape =F) %>%
  kable_classic_2(full_width = F) %>%
#   kable_styling(font_size = 20) %>%
 row_spec(0, bold = TRUE, font_size = 15) %>%
  footnote(general = "Results expressed in relation to the soil prepared according to the NF ISO 11464 standard, Cirad, Montpellier.",
           symbol = c("For available phosphorous, the Olsen method was used, best method for acid soils.")) %>%
 save_kable(
    "analyses_sol_table_innatura.png")

View(analyses_sol)

```


### Microbial analyses

Weights of samples before sterilization. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
Microbio <- read_excel("Natura_data/7_Microbio/Microbio.xlsx")
Microbio
```




