---
title: "Sciart"
author: "Marion Boisseaux"
date: "15/04/2022"
output: html_document
---

Here are the graphs related to our sciart book written with Antia Iglesias. 

# Root to shoot ratio 

Allocation accroding to drought treatments. When water is a limiting factor, metabolites involved with energy production and growth (especially sugars and amino acids) are shifted from shoots to roots. (Gargallo-Garriga et al 2014)

Attention!! T0, D1, D2 (only pteoff + symglo) no stem measurements. To add for root to shoot ratio. Ce n'est que les tendances pour l'instant.

Root:shoot biomass was log-transformed to meet the normality assumption.

E. falcata, V. surinamensis, and T. melinonii show a tendancy to invest more in their roots as the soil dries up compared to P. officinalis. For I. hostmannii, J. copaia and S. globulifera the pattern is not clear. 

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(ggpubr) #to add significance
library(rstatix)

RS_Natura <- googlesheets4::read_sheet("
https://docs.google.com/spreadsheets/d/1cJSPsAQScAIF9YBswBFNwoOyTdKMWEaj7E5st51Z0Ug/edit#gid=0", range = "Individuals")

RS_Natura <- RS_Natura %>% select(Code, Time, Genus, Species, RootShoot) %>% mutate(Treatment = "natura")

RS_Natura <- RS_Natura %>% rename(UniqueCode = Code)

RS_T0 <-  googlesheets4::read_sheet("
https://docs.google.com/spreadsheets/d/1hxXws0kkgQhkC3T023X6QZw5o-RAjnNo8c3_KcWfTpw/edit#gid=799954127", range = "destructif")

RS_T0 <- RS_T0 %>% select(UniqueCode, Time, Treatment, Species, RootShoot)

RS_D1 <-  googlesheets4::read_sheet("
https://docs.google.com/spreadsheets/d/1Vkmx3XCVR4L0QG22b_-zcIFutezT59gUlmr1ALW4V2Y/edit#gid=822184942", range = "destructif")

RS_D1 <- RS_D1 %>% select(UniqueCode, Time, Treatment, Species, RootShoot)

RS_D2 <- googlesheets4::read_sheet("
https://docs.google.com/spreadsheets/d/1SQekhd-T9yTKDTILUuHF0NY3Nlggy4enzFhSXLxJlK0/edit#gid=822184942", range = "destructif")

RS_D2 <- RS_D2 %>% select(UniqueCode, Time, Treatment, Species, RootShoot)

RS_D3 <- googlesheets4::read_sheet("
https://docs.google.com/spreadsheets/d/1al3U5pv2FQ0dWF6sbroB_6kJdzW1OnaLVpohykcKx7c/edit#gid=822184942", range = "destructif")

RS_D3 <- RS_D3 %>% select(UniqueCode, Time, Treatment, Species, RootShoot)

RS <- bind_rows(RS_Natura, RS_T0, RS_D1, RS_D2, RS_D3)

RS$Species[RS$Species == "Epe.fal"] <- "falcata"
RS$Species[RS$Species == "Iry.hos"] <- "hostmannii"
RS$Species[RS$Species == "Jac.cop"] <- "copaia"
RS$Species[RS$Species == "Pte.off"] <- "officinalis"
RS$Species[RS$Species == "Sym.off"] <- "globulifera"
RS$Species[RS$Species == "Tac.mel"] <- "melinonii"
RS$Species[RS$Species == "Vir.sur"] <- "surinamensis"

RS <- RS %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

RS$name <- paste(RS$Genus, RS$Species)

RS$Time <- as.factor(RS$Time)
RS$Treatment <- as.factor(RS$Treatment)

```

## Check normality of root shoot data

```{r}
#check normality

hisRS <- ggplot(RS) +
  aes(x = RootShoot) +
  geom_histogram(bins = 30L, fill = "#112446") +
  labs(
    x = "data",
    y = "frequence",
    title = "Check of normality of root:shoot"
  ) +
  theme_minimal()

shapiro.test(RS$RootShoot) # W = 0.76284, p-value < 2.2e-16 not normally distributed

logRS <- log10(RS$RootShoot)
shapiro.test(logRS) # W = 0.99117, p-value = 0.1013 # Root:shoot biomass logtransformed meets the normality assumption.

RS <- RS %>% mutate(logRS = log10(RS$RootShoot))

hisRS <- ggplot(RS) +
  aes(x = logRS) +
  geom_histogram(bins = 30L, fill = "#112446") +
  labs(
    x = "data",
    y = "frequence",
    title = "Check of normality of root:shoot"
  ) +
  theme_minimal()
```

## Statistical significances

All data. 

```{r}
# Statistical significances

RS_stats <- compare_means(logRS ~ Treatment, data = RS, method = "t.test", paired = FALSE, ref.group = "C0", group.by ="name") #there are multiple groups by i want to compare two groups : control and treatement each time.

#but missing: i want to compare co and treatment group within each time period. not across time periods. 

#3-way anova

RS %>%
  group_by(Time, name, Treatment) %>%
  get_summary_stats(logRS, type = "mean_sd")

#check outliers

RS %>%
  group_by(Time, name, Treatment) %>%
  identify_outliers(logRS) #there are some extreme outliers

#shapiro : test normality for each species too smal because sometimes less than 3 points (the control) but globally the distribution of logRS is normal. QQ plots show that all the points fall approximately along the reference line, we can assume normality. 

ggqqplot(RS, "logRS", ggtheme = theme_bw()) +
  facet_grid(Time + Treatment ~ name, labeller = "label_both")

#anova II-way

#For repeated measure anova III, you need complete observations for each time point, before and after treatment ...; arghhh so that's why it doesn't work. The only way is to repeat a Anova II

anova_test(data=RS,dv=logRS,between=c(name,Time))
anova_test(data=RS,dv=logRS,between=c(name,Treatment))


```

## Species per species stat compare means


```{r}
#eperua falcata

epefal <- RS %>% filter(name %in% "Eperua falcata")

epefalt21 <- epefal %>% filter(Time %in% "t21")
epefalt27 <- epefal %>% filter(Time %in% "t27")
epefalt71 <- epefal %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = epefalt21)#ns
t.test(logRS ~ Treatment, data = epefalt27)#not enough observation
t.test(logRS ~ Treatment, data = epefalt71)#not enough observation

#to test significance 
#stat.test <- epefalt71 %>%
 # t_test(logRS ~ Treatment) %>%
  #adjust_pvalue(method = "BH") %>%
  #add_significance()
#stat.test

#iryanthera hostmannii

iryhos <- RS %>% filter(name %in% "Iryanthera hostmannii")


iryhost21 <- iryhos %>% filter(Time %in% "t21")
iryhost27 <- iryhos %>% filter(Time %in% "t27")
iryhost71 <- iryhos %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = iryhost21)#ns
t.test(logRS ~ Treatment, data = iryhost27)#ns
t.test(logRS ~ Treatment, data = iryhost71)#ns

# jacaranda copaia

jaccop <- RS %>% filter(name %in% "Jacaranda copaia")

jaccopt21 <- jaccop %>% filter(Time %in% "t21")
jaccopt27 <- jaccop %>% filter(Time %in% "t27")
jaccopt71 <- jaccop %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = jaccopt21)#ns
t.test(logRS ~ Treatment, data = jaccopt27)#ns
t.test(logRS ~ Treatment, data = jaccopt71)#ns


#pterocarpus officinalis

pteoff <- RS %>% filter(name %in% "Pterocarpus officinalis")


pteofft21 <- pteoff %>% filter(Time %in% "t21")
pteofft27 <- pteoff %>% filter(Time %in% "t27")
pteofft71 <- pteoff %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = pteofft21)#ns
t.test(logRS ~ Treatment, data = pteofft27)#ns
t.test(logRS ~ Treatment, data = pteofft71)#pvalue 0.0246 *

#Tachigali melinonii

tacmel <- RS %>% filter(name %in% "Tachigali melinonii")

tacmelt21 <- tacmel %>% filter(Time %in% "t21")
tacmelt27 <- tacmel %>% filter(Time %in% "t27")
tacmelt71 <- tacmel %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = tacmelt21)#ns
t.test(logRS ~ Treatment, data = tacmelt27)#ns
t.test(logRS ~ Treatment, data = tacmelt71)#  p-value = 0.03071 *

# symphonia globulifera

symglo <- RS %>% filter(name %in% "Symphonia globulifera")


symglot21 <- symglo %>% filter(Time %in% "t21")
symglot27 <- symglo %>% filter(Time %in% "t27")
symglot71 <- symglo %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = symglot21)#ns
t.test(logRS ~ Treatment, data = symglot27)#ns
t.test(logRS ~ Treatment, data = symglot71)#ns


#Virola surinamensis

virsur <- RS %>% filter(name %in% "Virola surinamensis")

virsurt21 <- virsur %>% filter(Time %in% "t21")
virsurt27 <- virsur %>% filter(Time %in% "t27")
virsurt71 <- virsur %>% filter(Time %in% "t71")

t.test(logRS ~ Treatment, data = virsurt21)#ns
t.test(logRS ~ Treatment, data = virsurt27)#ns
t.test(logRS ~ Treatment, data = virsurt71)#ns

```

## Plot

```{r}
# plot all 

RS_plot <- ggplot(RS) +
  aes(x = Time, y = RootShoot, fill = Treatment) +
  geom_boxplot(shape = "circle") +
  scale_fill_manual(
    values = list(
      C0 = "#0725CB",
      D1 = "#1BE04A",
      D2 = "#D4EB20",
      D3 = "#E00F0F",
      natura = "#FF61C3"
    )
  ) +
  labs(
    x = "Time",
    y = "Root to shoot ratio",
    title = "Root to shoot ratio of 7 tropical tree species across different drought treatments"
  ) +
  theme_minimal() +
  facet_wrap(vars(name), scales = "free_y")
# plot log

RS_nonatura <- RS %>% filter(!(Time %in% "natura"))

log_plot <- ggplot(RS_nonatura) +
  aes(x = Time, y = logRS, fill = Treatment) +
  geom_boxplot(shape = "circle") +
  scale_fill_manual(
    values = list(
      C0 = "#0725CB",
      D1 = "#1BE04A",
      D2 = "#D4EB20",
      D3 = "#E00F0F",
      natura = "#FF61C3"
    )
  ) +
  labs(
    x = "Time",
    y = "Log of Root to shoot ratio",
    title = "Root to shoot ratio of 7 tropical tree species across different drought treatments"
  ) +
  theme_minimal() +
  facet_wrap(vars(name), scales = "free_y")

#  Add p-value cannot add it though 
RSplot + stat_compare_means()
```

## For Sciart publication 

Tachigali or Pterocarpus where there are significant differences

```{r}
pteoff <- RS %>% filter(name %in% "Pterocarpus officinalis")

pteoff <- pteoff %>% filter(!Time %in% "t0")

t.test(logRS ~ Treatment, data = pteofft21)#ns
t.test(logRS ~ Treatment, data = pteofft27)#ns
t.test(logRS ~ Treatment, data = pteofft71)#pvalue 0.0246 *

pteoff %>%
 filter(!(Time %in% "natura")) %>%
 filter(!(Treatment %in% "natura")) %>%
 ggplot() +
  aes(x = Time, y = RootShoot, fill = Treatment) +
  geom_boxplot(shape = "circle") +
  scale_fill_manual(
    values = list(
      C0 = "#0725CB",
      D1 = "#1BE04A",
      D2 = "#D4EB20",
      D3 = "#E00F0F"
    )) +
  labs(
    x = "Time",
    y = "Root to shoot ratio",
    title = "Root to shoot ratio of Pterocarpus officinalis across different drought treatments"
  ) + 
  theme_minimal() + 
  stat_compare_means()

```

#All data for graphs combined

```{r}

library(dplyr)

T0 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1hxXws0kkgQhkC3T023X6QZw5o-RAjnNo8c3_KcWfTpw/edit#gid=799954127", range = "non_destructif")

T0 <- T0 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T21 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1Vkmx3XCVR4L0QG22b_-zcIFutezT59gUlmr1ALW4V2Y/edit#gid=258591157",range = "non_destructif")

T21 <- T21 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)
 
T27 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SQekhd-T9yTKDTILUuHF0NY3Nlggy4enzFhSXLxJlK0/edit#gid=822184942",range = "non_destructif")

T27 <- T27 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T51 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lmgpcbXdVcC2de3_-uc3g0w_P8Ab7z1m4faLhd2EmXI/edit#gid=539250691", range = "non_destructif")

T51 <- T51 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T57 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rh34QE6izuGEnB4eQFLn4lv5oEf2CaFscT1Tsjc6NQA/edit#gid=822184942", range = "non_destructif")

T57 <- T57 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T71 <- 
googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1al3U5pv2FQ0dWF6sbroB_6kJdzW1OnaLVpohykcKx7c/edit#gid=258591157", range = "non_destructif")

T71 <- T71 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T101 <- 
googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1ItJdPwjk5uwm6xcuP79dnaRvxP88lwVACGWBStx0NvI/edit#gid=0", range = "non_destructif")

T101 <- T101 %>% select(Time, Treatment, Species, Chloro, gs, FvFm, Asat)

T101$Chloro <- as.numeric(T101$Chloro)
T101$gs <- as.numeric(T101$gs)
T101$FvFm <- as.numeric(T101$FvFm)

ALL <- bind_rows(T0, T21, T27, T51, T57, T71, T101)


```

# ALL non destructive data

```{r}
ALL$Species[ALL$Species == "Epe.fal"] <- "falcata"
ALL$Species[ALL$Species == "Iry.hos"] <- "hostmannii"
ALL$Species[ALL$Species == "Jac.cop"] <- "copaia"
ALL$Species[ALL$Species == "Pte.off"] <- "officinalis"
ALL$Species[ALL$Species == "Sym.off"] <- "globulifera"
ALL$Species[ALL$Species == "Tac.mel"] <- "melinonii"
ALL$Species[ALL$Species == "Vir.sur"] <- "surinamensis"

ALL <- ALL %>% mutate(Genus = 'NA')

ALL <- ALL %>%
  mutate(Genus = case_when(
    Species == 'falcata' ~ 'Eperua',
    Species == 'hostmannii' ~ 'Iryanthera',
    Species == 'copaia' ~ 'Jacaranda',
    Species == 'officinalis' ~ 'Pterocarpus',
    Species == 'globulifera' ~ 'Symphonia',
    Species == 'melinonii' ~ 'Tachigali',
    Species == 'surinamensis' ~ 'Virola',
    TRUE ~ Genus)
  )

ALL$name <- paste(ALL$Genus, ALL$Species)


```

## Chlorophyll content

From equations developped by Coste 2008. 
y is the chlorophyll in $\mu mol . m²$

Eperua falcata : y= 0.124x² -0.448x +151.9
Symphonia globulifera : y = 0.083x² +6.504x +47.08
Tachigali melinonii : y = 0.186x²+3.370x+169.3

```{r Chloro}

Epefal_Chloro <- ALL %>%
 filter(name %in% "Eperua falcata") 

Epefal_Chloro <- mutate(Epefal_Chloro, CC= 0.124 * Chloro^2 -0.448 *Chloro +151.9 )
  
Symglo_Chloro <- ALL %>%
 filter(name %in% "Symphonia globulifera") 

Symglo_Chloro <- mutate(Symglo_Chloro, CC= 0.083 * Chloro^2 +6.504 * Chloro +47.08 )

Tacmel_Chloro <- ALL %>%
 filter(name %in% "Tachigali melinonii") 

Tacmel_Chloro <- mutate(Tacmel_Chloro, CC= 0.186 * Chloro^2 +3.37 * Chloro +169.3 )



  
```


## Cholorphyll fluorescence

Chlorophyll fluorescence was measured as the ratio of variable to maximum fluorescence (FV/FM) in the convention of Maxwell and Johnson (2000). FV/FM measures the maximum quantum efficiency of PSII photochemistry (Genty et al., 1989)

FV/FM is considered a sensitive indicator of photosynthetic performance (Maxwell and Johnson, 2000) and has been used to monitor photosynthetic function during severe drought stress (e.g. Ings et al., 2013; García de la Serrana et al., 2015; Chen et al., 2016; Yao et al., 2018). Optimal FV/FM values are ~0.8 (Björkman and Demmig, 1987). FV/FM before drought did not significantly differ among families or treatment *(P > 0.05).* We used FV/FM as a rapid, nondestructive method to compare relative differences in effects of severe drought among groups.
