---
title: "Dryer_natura_Ptlp"
author: "Marion Boisseaux"
date: "22/07/2021"
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: 5
---

We assessed the leaf turgor loss point, $\pi_{tlp}$ in MPa, from a previously established relationship with the osmotic potential at full hydration, $\pi_{osm}$ in MPa. $\pi_{osm}$ is linked to the equilibrium solute concentration value $C_0$ (in mmol.kg^{-1}) directly measured with a vapor pressure osmometer (Vapro 5600, Wescor, Logan, UT). This is referred as the *osmometer method* (Bartlett et al. 2012a; Maréchaux et al. 2016).

# Uploading Ptlp data
 
Uploading Ptlp data from vapro excel files for all the field days of DRYER natura 2021.

```{r}
knitr::opts_chunk$set(echo = TRUE)


library(plyr)
library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
library(ggplot2)
library(readxl)
library(forcats)
library(questionr)
path <- "Rawdata/5_Ptlp"


myfiles <- list.files(path=path, pattern = "*.xlsx", full.names = TRUE ) #it will read the file with * being the replaced value each time

data = ldply(myfiles, read_excel)

data <- as_tibble(data)
data

```

#Tidying dataframe

```{r}
data <- select(data, - Calibration_Date, - Contamination_Level, - `Scan?` )

data$C0 <- as.numeric(data$C0)
  
```

#Calculating Posm et Ptlp

The equilibrium solute concentration value $C_0$ (in mmol.kg^{-1}) was recorded from the osmometer when the difference between two consecutive measurements fell below 5 mmol.kg^{-1}. This value was converted to $\pi_{osm}$ values using the van't Hoff equation:  
 
 $\pi_{osm}$ = $(-2.5/1000)$x$C_0$
 
  where the numerator of the first term represents RxT = 2.5 L.MPa.mol^{-1}^ at 25°C, with R the ideal gas constant and T the temperature in Kelvin degrees.
  
The value $\pi_{osm}$ was then converted to $\pi_{tlp}$ using the following equation:  
 
$\pi_{tlp}$= ( 0.799x $\pi_{osm}$ ) -0.665

```{r}
# Calculate new numeric variables with math formulas

data <- mutate(data, Posmo = (-2.5/1000)* as.numeric(C0))
data <- mutate(data, Ptlp=(0.799*Posmo)-0.665)

view(data)

```



#Selecting next run or leaf if first did not work

```{r}

Ptlp_clean <- data %>% filter(Ptlp !=0) %>% distinct(Code, .keep_all = TRUE)




for (i in 1:length(Ptlp$Nr_Leaf)) {
    
  if (is.na(Ptlp$Ptlp[i])) {
    #Ptlp$Ptlp[i]<- Ptlp$Ptlp[i+1]
    
  
  }
  else {
    print("wow, that's awesome")
  }
}

#-------------------------------

for each Code

variable Ptlp takes value:

for Ptlp$Nr_Leaf = 1 , if variable Ptlp has value, 'then' keep it
                       if variable Ptlp has NA , 'then' switch to Ptlp$Nr_Leaf=2


for Ptlp$Nr_Leaf = 2 , if variable Ptlp has value, 'then' keep it
                       if variable Ptlp has NA , 'then' keep NA



```

## Mean species values


```{r echo=FALSE}

summarise(Ptlp_clean$Species_Name)

count = count(Ptlp_clean, Species_Name)

group_species<- Ptlp_clean %>% 
  group_by(Species_Name) %>% 
  summarize(mean_Ptlp=mean(Ptlp))
kable(group_species,
      col.names= c("Species_Name", "Mean $\\pi{tlp}$ values"),
      align = 'c',
      label="Mean pi_{tlp} values for 24 species")

group_species <- mutate(group_species, n=count)

ggplot(group_species) +
  aes(x = Species_Name, y = mean_Ptlp) +
  geom_boxplot(shape = "circle", fill = "#454611") +
  labs(
    x = "Species ",
    y = "Pressure at turgor loss point (MPa)",
    title = "Mean Ptlp per species"
  ) +
  theme_minimal()
```
